gratia: An R package for exploring generalized additive models

### 2025-08-07 README.Rmd
add a section on citing gratia
clean ups for release

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
library("mgcv")
library("gratia")
```

@@

@@

```{r draw-gam-figure, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide", message = FALSE}
df1 <- data_sim("eg1", n = 400, seed = 42)
m1 <- gam(y ~ s(x0) + s(x1) + s(x2) + s(x3), data = df1, method = "REML")
draw(m1, residuals = TRUE)
```

```{r draw-gam-figure-2d, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide", message = FALSE}
df2 <- data_sim("eg2", n = 1000, seed = 42)
m2 <- gam(y ~ s(x, z), data = df2, method = "REML")
draw(m2)
```

```{r appraise-figure, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide"}
appraise(m1)
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = "ragg_png",
  dpi = 96
)
options(tibble.print_min = 5, tibble.print_max = 5)
library("mgcv")
library("gratia")
```

@@

## Citation

If you use *gratia* in your work, please cite the package using:

Simpson, G. L., (2024). gratia: An R package for exploring generalized additive
models. *Journal of Open Source Software*, **9**(104), 6962,
<https://doi.org/10.21105/joss.06962>

@@

```{r draw-gam-figure, fig.height = 6, fig.width = 9, echo = FALSE, fig.show = "hide", message = FALSE}
df1 <- data_sim("eg1", n = 400, seed = 42)
m1 <- gam(y ~ s(x0) + s(x1) + s(x2) + s(x3), data = df1, method = "REML")
draw(m1, residuals = TRUE, rug = FALSE)
```

```{r draw-gam-figure-2d, fig.height = 6, fig.width = 9, echo = FALSE, fig.show = "hide", message = FALSE}
df2 <- data_sim("eg2", n = 1000, seed = 42)
m2 <- gam(y ~ s(x, z), data = df2, method = "REML")
draw(m2)
```

```{r appraise-figure, fig.height = 6, fig.width = 9, echo = FALSE, fig.show = "hide"}
appraise(m1)
```
